### 2015-01-02 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report

To calculate the total fire size, the appropriate burning area of the basement needed to be determined. Based on the floor plan of the structure and post-incident images, two distinct fires were considered: 1 source in the basement bathroom and 1 source in the basement kitchen. The bathroom fire was estimated to be comprised of wood paneling along the four walls (17.3~m$^2$ or 186~ft$^2$) and wood subfloors and studs along the ceiling (2.9~m$^2$ or 31~ft$^2$). This results in 20.2~m$^2$ (217~ft$^2$) of wood burning surface area at 50~kW/m$^2$ or a 1~MW energy release rate.

The remainder of the combustable load in the basement was lumped into the localized kitchen fire.

>>>>

To calculate the total fire size, the appropriate burning area of the basement needed to be determined. Based on the floor plan of the structure and post-incident images, two distinct fires were considered: 1 source in the basement bathroom and 1 source in the basement kitchen. The bathroom fire was estimated to be comprised of wood paneling along the four walls (17.3~m$^2$ or 186~ft$^2$) and wood subfloors and studs along the ceiling (2.9~m$^2$ or 31~ft$^2$). This results in 20.2~m$^2$ (217~ft$^2$) of wood burning surface area at 50~kW/m$^2$ or a 1~MW energy release rate. The remainder of the wood combustable load in the basement was lumped into the localized kitchen fire. The ceiling and wall areas were included in the basement kitchen and main living area totally approximately 86~m$^2$ (926~ft$^2$). This would result in a 4.3~MW fire.

Initial simulations were conducted with the two point location fires totaling 5.3~MW, however, the fire behavior did not align with observations made during the fire incident or post-incident images. Specifically there was insufficient fuel in the basement to drive the basement to an underventilated condition. At the time of the fire the structure was unoccupied~\cite{PGCounty2013}, there were additional fuels that were not accounted for: transient fuels, sparse kitchen cabinetry, and an unknown bathroom vanity among other fuels. A second reason is that the 50~kW/m$^2$ HRRPUA used to estimate the first size does not account for an observed increase in burning rate during wind driven fires~\cite{madrzykowski2009fire,kerber2009fire}. It is not clear how to quantify the impact of wind on burning rate within a structure from first principles, so several iterations of the model with increased fire sizes were run. The final estimated fire size was a 1.8~MW fire in the bathroom and a 6.75~MW fire in the kitchen. This resulted in a total peak specified fire size of 8.55~MW.
